Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-07 appendix.tex
mkl edit of sec 5.3, 6.0, 6.1, partial 7

\subsection{Maximum critical cooling time}\label{max_cool}
 % {\bf [at the moment for reference
 %  only, not to be included in final version]}\\
Consider the simplified dispersion relations for marginal stability,
Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2}. Writing 
$X= \hat{\omega}\khat$, $\theta = (hq\khat)^2\leq1$ and  treating $M$ as a
continuous variable, we find from Eq. \ref{relax_cond_simp1} that 
%\begin{align}
%  &x^4  = x^2 + M(M+1)(1-\theta), \label{simp1}\\
%  &x^2  = \frac{\gamma-1}{h q}\beta_c (1+2M)^2x - 2M(M+1)\label{simp2},
%\end{align}
%where and
\begin{align}
  2 X \frac{d X}{dM} = \frac{X^2(1-\theta)(2M+1)}{X^2 +
  2M(M+1)(1-\theta)}, 
\end{align}
and from Eq. \ref{relax_cond_simp2} that
\begin{align}
  2X\frac{dX}{dM} = \left[X^2 +
  2M(M+1)\right]\left(\frac{d\ln{\beta_c}}{dM} + \frac{4}{2M+1} +
  \frac{d\ln{X}}{dM}\right) - 2(2M+1). 
\end{align}
We eliminate $dX/dM$, making use of Eq. \ref{relax_cond_simp1} in the process, to obtain 
\begin{align}
  (2M+1)\frac{d\ln{\beta_c}}{dM} %= \frac{\mathcal{N}}{\mathcal{D}}, 
  = -\frac{(1-\theta)M(M+1)\left[ 2(2M+1)^2 + 12X^2\right]
  + (3+\theta)X^2}{2 \left[X^2 +
  2M(M+1)(1-\theta)\right]\left[X^2 + 2M(M+1)\right]}.  
\end{align}
%where the denominator $\mathcal{D}$ is
%\begin{align}
%\mathcal{D} = 2 \left[X^2 +
 % 2M(M+1)(1-\theta)\right]\left[X^2 + 2M(M+1)\right]>0, 
%\end{align}
%and the numerator $\mathcal{N}$ is 
%\begin{align}
 % \mathcal{N} = -(1-\theta)\left[ 2M(M+1)(2M+1)^2 + 12X^2M(M+1)\right]
 % - (3+\theta)X^2 < 0.
%\end{align}
Hence,
\begin{align}
  \frac{d\beta_c}{dM}<0, 
\end{align}
for all $M\geq 0$ if $\theta\leq 1$. This implies 
$\mathrm{max}(\beta_c)$ occurs at $M=0$.

>>>>

\subsection{Maximum critical cooling time}\label{max_cool}   
Here we show that, under appropriate conditions, the maximum critical 
cooling time is that for the $M=0$ or fundamental mode. This allows
us to focus on the fundamental mode to obtain an overall cooling
requirement for the VSI.

Consider the simplified dispersion relations for marginal stability,
Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2}. We write 
$X= \hat{\omega}\khat$, $\theta = (hq\khat)^2$ and  
treat $M$ as a continuous variable. We find from
Eq. \ref{relax_cond_simp1} that  
%\begin{align}
%  &x^4  = x^2 + M(M+1)(1-\theta), \label{simp1}\\
%  &x^2  = \frac{\gamma-1}{h q}\beta_c (1+2M)^2x - 2M(M+1)\label{simp2},
%\end{align}
%where and
\begin{align}
  2 X \frac{d X}{dM} = \frac{X^2(1-\theta)(2M+1)}{X^2 +
  2M(M+1)(1-\theta)}, 
\end{align}
and from Eq. \ref{relax_cond_simp2} that
\begin{align}
  2X\frac{dX}{dM} = \left[X^2 +
  2M(M+1)\right]\left(\frac{d\ln{\beta_c}}{dM} + \frac{4}{2M+1} +
  \frac{d\ln{X}}{dM}\right) - 2(2M+1). 
\end{align}
We eliminate $dX/dM$, making use of Eq. \ref{relax_cond_simp1} in the process, to obtain 
\begin{align}
  (2M+1)\frac{d\ln{\beta_c}}{dM} %= \frac{\mathcal{N}}{\mathcal{D}}, 
  = -\frac{(1-\theta)M(M+1)\left[ 2(2M+1)^2 + 12X^2\right]
  + (3+\theta)X^2}{2 \left[X^2 +
  2M(M+1)(1-\theta)\right]\left[X^2 + 2M(M+1)\right]}.  
\end{align}
%where the denominator $\mathcal{D}$ is
%\begin{align}
%\mathcal{D} = 2 \left[X^2 +
 % 2M(M+1)(1-\theta)\right]\left[X^2 + 2M(M+1)\right]>0, 
%\end{align}
%and the numerator $\mathcal{N}$ is 
%\begin{align}
 % \mathcal{N} = -(1-\theta)\left[ 2M(M+1)(2M+1)^2 + 12X^2M(M+1)\right]
 % - (3+\theta)X^2 < 0.
%\end{align}
Hence,
\begin{align}\label{dbeta_dm}
  \frac{d\beta_c}{dM}<0, 
\end{align}
for all $M\geq 0$ if $\theta\leq 1$, which imply 
$\mathrm{max}(\beta_c)$ occurs at $M=0$. For fixed $\khat$ the
condition $\theta\leq 1$ can be satisfied in sufficiently thin disks.
This means that if $\beta>\beta_c(M=0)\equiv\beta_\mathrm{crit}$, then
all such modes will be stabilized.

This result highlights the importance of the fundamental mode  
--- it is the most difficult mode to stabilize with finite
cooling. Furthermore, for $M=0$ we may obtain the expression  
for $\beta_\mathrm{crit}$ from the dispersion relations 
Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2} without  
assuming it is much less than unity from the onset or place
restrictions on $\theta$.

% restrictions on $| h q \khat|$.

### 2015-05-07 application.tex
mkl edit of sec 5.3, 6.0, 6.1, partial 7

@@

Since the VSI is characterized by vertically-elongated,
radially-narrow disturbances, we retain only the radial derivatives in Eq. \ref{diff_cool_proper}.
Thus, in the radially local approximation, we have
\begin{align}\label{diff_cool_approx}
  % \frac{P}{\rho T C_v} \nabla\cdot\left(k_\mathrm{rad}\nabla\delta
  %  T\right) &
  \delta\Lambda_\mathrm{diff} \approx %-\frac{k_\mathrm{rad}}{\rho
  % C_v}k_x^2P\left(\frac{\delta T}{T}\right)%\notag\\
  % \equiv 
  %-\eta k_x^2 \left(\delta P - \frac{P}{\rho}\delta\rho\right) =
  -\eta k_x^2 P \frac{\delta T}{T}, %=
  %-\frac{P}{t_\mathrm{diff}}\frac{\delta T}{T},
  %\frac{P}{t_\mathrm{diff}}\left(\frac{delta T}{T}\right), 
\end{align}
where the radiative diffusion coefficient is
\begin{align}\label{eta_def}
  \eta \equiv {k_\mathrm{rad} \over \rho C_v} = \frac{16\sigma_s T^3}{3\kappa_d\rho^2 C_v}, 
\end{align}
and $\sigma_s$ is the Stefan-Boltzmann constant.

The thermal relaxation  timescale (defined in Eq. \ref{thermal_relax}) 
for radiative diffusion is thus 
\begin{align}\label{tc_diff_cool} 
  t_\mathrm{diff} = \frac{1}{\eta k_x^2}.%\equiv \frac{\OmK^{-1}}{\hat{\eta}\khat^2}, 
\end{align}

In the optically thin regime, $l\ll 
l_\mathrm{rad}$, thermal relaxation operates by ``Newtonian cooling."
The cooling time is independent of $l$ and 
inversely proportional to the opacity, $t_\mathrm{thin} \propto 1/\kappa_d$. 
Specifically 
\begin{align}
  t_\mathrm{thin} = \frac{l_\mathrm{rad}^2}{3\eta},
\end{align}
and $t_\mathrm{thin}$ does not depend on $\rho$ (because $\kappa_d$ depends on $T$ only).

@@

\subsubsection{PPD cooling times}\label{toy_relax}
In a vertically isothermal disk with surface density $\Sigma = \rho_0/\sqrt{2\pi}H$, 
the dimensionless thermal
relaxation time $\beta$ becomes 
\begin{align}\label{real_beta}
  \beta(r,z;\khat) \equiv t_c\OmK =
  % \frac{1}{\hat{\eta}}\left[\frac{l_\mathrm{rad}^2}{3H^2}
  %   + \frac{\hat{\rho}^2(z)}{2\pi\khat^2}\right]  \simeq
  \frac{\Sigma^2\OmK}{\eta\rho^2}\left[\frac{1}{3\kappa_d^2\Sigma^2} 
    + \frac{\hat{\rho}^2(z)}{2\pi \khat^2}\right].
\end{align}
where $\hat{\rho} = \rho/\rho_0$.  The first and second terms in square brackets represent the optically thin and thick cooling regimes, respectively.

We adopt the Minimum Mass Solar Nebula
(MMSN) disk model of \cite{chiang10} which specifies
\emph{note that the normalizations are suppressed b/c I can't see where we used them.  We should only add back in if we decide to use them.}
\begin{subequations}
\begin{align}
\label{mmsn_sigma}
  \Sigma &= 2200 %\hat{\Sigma}\left(\frac{r}{\mathrm{AU}}\right)^{-3/2}
 r_\mathrm{AU}^{-3/2} \mathrm{g}\,\mathrm{cm}^{-2},  \\
 T &= 120%\hat{T}\left(\frac{r}{\mathrm{AU}}\right)
  r_\mathrm{AU}^{-3/7} \mathrm{K}, \label{mmsn_temp}  
\end{align}\end{subequations}
with $r_\mathrm{AU}\equiv r/\mathrm{AU}$.  This model has $q = -3/7$, $p = -39/14$ and $h  = 0.034 r_\mathrm{AU}^{2/7}$, using $\mu = 2.33$ and the above relation between $\Sigma$ and $\rho_0 \propto r^p$.

For the dust opacity we adopt the \citet{bell94} law with $\kappa_d \propto T^2$, giving
\begin{align}
 \kappa_d %&= 2 \hat{\kappa}_d \left(\frac{T}{100\mathrm{K}}\right)^2 \mathrm{cm}^2\,\mathrm{g}^{-1}
    =
   2.88\hat{\kappa}_d r_\mathrm{AU}^{-6/7}\mathrm{cm}^2\,\mathrm{g}^{-1},   
\end{align}
where the opacity normalication factor, $\hat{\kappa}_d$, scales with the ratio of small dust to gas;  $\hat{\kappa}_d = 1$ is our fiducial case.

@@

This comparison strictly valid only for optically thin cooling which is independent of height,
as assumed in the derivation of $\beta_\mathrm{crit}$.  This condition typically holds in the outer disk.  
Fig. \ref{beta_compare} shows that a  $\khat=30$ perturbation at 50 AU has vertically constant $\beta$. 
 Furthermore, since $\beta < \beta_\mathrm{crit}$, the mode is unstable.

For optically thick cooling, $\beta$ varies with height, complicating the comparison with $\beta_\mathrm{crit}$.   
At 5 AU, Fig. \ref{beta_compare} shows that cooling times are long in the midplane with $\beta > \beta_\mathrm{crit}$.
However, since $\beta < \beta_\mathrm{crit}$ away from the midplane, we require the analysis of \S\ref{vsi_mmsn_grow} to determine if the VSI can grow.  (That analysis will show that growth is stongly suppressed for this case.)  We proceed with the awareness that optically thick regions in the inner disk are a complication, but that we can reasonably expect VSI growth if $\beta < \beta_\mathrm{crit}$ at all heights.

@@

We find that the most important factor for VSI growth is the opacity.  With a smaller opacity, $\hat{\kappa}_d = 0.1$, growth is suppressed at all radii, as shown in the top panels of Fig.\ \ref{mmsn_bcrit_bcool}.  Since optically thin cooling is too slow in this case, optically thick cooling -- above the floor set by optically thin cooling -- is also too slow.

>>>>

% As an application of our linear models, we estimate where in a
% PPD do the thermodynamic conditions allow the VSI to
% operate. We first model the cooling time $t_c$ based on realistic
% disk properties, which yields a non-uniform dimensionless cooling
% time $\beta(r,z;\khat)$. We then compare this to the critical cooling time
% $\beta_\mathrm{crit}$ derived above. Finally, we explicitly compute 
% linear growth rates numerically, using $\beta(r,z;\khat)$, to
% characterize growth times expected in a typical PPD.

@@

Since the VSI is characterized by vertically-elongated,
radially-narrow disturbances, we retain only the radial derivatives of
the perturbations in Eq. \ref{diff_cool_proper}. 
Thus, in the radially local approximation, we have
\begin{align}\label{diff_cool_approx}
  % \frac{P}{\rho T C_v} \nabla\cdot\left(k_\mathrm{rad}\nabla\delta
  %  T\right) &
  \delta\Lambda_\mathrm{diff} \simeq %-\frac{k_\mathrm{rad}}{\rho
  % C_v}k_x^2P\left(\frac{\delta T}{T}\right)%\notag\\
  % \equiv 
  %-\eta k_x^2 \left(\delta P - \frac{P}{\rho}\delta\rho\right) =
  -\eta k_x^2 P \frac{\delta T}{T}, %=
  %-\frac{P}{t_\mathrm{diff}}\frac{\delta T}{T},
  %\frac{P}{t_\mathrm{diff}}\left(\frac{delta T}{T}\right), 
\end{align}
where the radiative diffusion coefficient is
\begin{align}\label{eta_def}
  \eta \equiv {k_\mathrm{rad} \over \rho C_v} = \frac{16\sigma_s T^3}{3\kappa_d\rho^2 C_v}, 
\end{align}
and $\sigma_s$ is the Stefan-Boltzmann constant. 
The thermal relaxation  timescale (defined in Eq. \ref{thermal_relax}) 
for radiative diffusion is thus 
\begin{align}\label{tc_diff_cool} 
  t_\mathrm{diff} = \frac{1}{\eta k_x^2}.%\equiv \frac{\OmK^{-1}}{\hat{\eta}\khat^2}, 
\end{align}

In the optically thin regime, $l\ll 
l_\mathrm{rad}$, thermal relaxation operates by `Newtonian cooling'.
The cooling time is independent of $l$ and 
inversely proportional to the opacity, $t_\mathrm{thin} \propto 1/\kappa_d$. 
Specifically 
\begin{align}
  t_\mathrm{thin} = \frac{l_\mathrm{rad}^2}{3\eta},
\end{align}
and $t_\mathrm{thin}$ does not depend on $\rho$ (because our adopted
$\kappa_d$ depends on $T$ only, see below).

@@

\subsubsection{PPD cooling times}\label{toy_relax}
In a vertically isothermal disk with surface density $\Sigma = \rho_0\sqrt{2\pi}H$, 
the dimensionless thermal
relaxation time $\beta$ becomes 
\begin{align}\label{real_beta}
  \beta(r,z;\khat) \equiv t_c\OmK =
  % \frac{1}{\hat{\eta}}\left[\frac{l_\mathrm{rad}^2}{3H^2}
  %   + \frac{\hat{\rho}^2(z)}{2\pi\khat^2}\right]  \simeq
  \frac{\Sigma^2\OmK}{\eta\rho^2}\left[\frac{1}{3\kappa_d^2\Sigma^2} 
    + \frac{\hat{\rho}^2(z)}{2\pi \khat^2}\right].
\end{align}
where $\hat{\rho} = \rho/\rho_0$.  The first and second terms in
square brackets represent the optically thin and thick cooling
regimes, respectively.

We adopt the Minimum Mass Solar Nebula
(MMSN) disk model of \cite{chiang10} which specifies
% \emph{note that the normalizations are suppressed b/c I can't see where we used them.  We should only add back in if we decide to use them.}
\begin{subequations}
\begin{align}
\label{mmsn_sigma}
  \Sigma &= 2200 %\hat{\Sigma}\left(\frac{r}{\mathrm{AU}}\right)^{-3/2}
 r_\mathrm{AU}^{-3/2} \mathrm{g}\,\mathrm{cm}^{-2},  \\
 T &= 120%\hat{T}\left(\frac{r}{\mathrm{AU}}\right)
  r_\mathrm{AU}^{-3/7} \mathrm{K}, \label{mmsn_temp}  
\end{align}\end{subequations}
with $r_\mathrm{AU}\equiv r/\mathrm{AU}$. This model has $q = -3/7$,
$p = -39/14$ and $h  = 0.022 r_\mathrm{AU}^{2/7}$, using $\mu = 2.33$
and the above relation between $\Sigma$ and $\rho_0 \propto r^p$.

For the dust opacity we adopt the \citet{bell94} law with $\kappa_d
\propto T^2$, giving 
\begin{align}
 \kappa_d %&= 2 \hat{\kappa}_d \left(\frac{T}{100\mathrm{K}}\right)^2 \mathrm{cm}^2\,\mathrm{g}^{-1}
    =
   2.88\hat{\kappa}_d r_\mathrm{AU}^{-6/7}\mathrm{cm}^2\,\mathrm{g}^{-1},   
\end{align}
where the opacity normalization factor, $\hat{\kappa}_d$, scales with
the ratio of small dust to gas;  $\hat{\kappa}_d = 1$ is our fiducial
case.

@@

This comparison is strictly valid only for optically thin cooling
which is independent of height, as assumed in the derivation of
$\beta_\mathrm{crit}$.  This condition typically holds in the outer
disk.   Fig. \ref{beta_compare} shows that a  $\khat=30$ perturbation
at 50AU has vertically constant $\beta$. Furthermore, since $\beta <
\beta_\mathrm{crit}$, the disturbance would be unstable.

For optically thick cooling, $\beta$ varies with height, complicating
the comparison with $\beta_\mathrm{crit}$.    
At 5AU, Fig. \ref{beta_compare} shows that cooling times are long in
the midplane with $\beta > \beta_\mathrm{crit}$. 
However, since $\beta < \beta_\mathrm{crit}$ away from the midplane,
we require the analysis of \S\ref{vsi_mmsn_grow} to determine if the
VSI can grow.  (That calculation will show that growth is stongly
suppressed for this case.)  We proceed with the awareness that
optically thick regions in the inner disk are a complication, but that
we can reasonably expect VSI growth if $\beta < \beta_\mathrm{crit}$
at all heights.

@@

We find that the most important factor for VSI growth is the opacity.
With a smaller opacity, $\hat{\kappa}_d = 0.1$, growth is suppressed
at all radii, as shown in the top panels of Fig.\
\ref{mmsn_bcrit_bcool}.  Since optically thin cooling is too slow in
this case, optically thick cooling --- above the floor set by optically
thin cooling --- is also too slow.

### 2015-05-07 linear_adia.tex
re-writing sec 7 in progress
mkl edit of sec 5.3, 6.0, 6.1, partial 7

\subsection{An upper limit to the cooling time}\label{iso_vsi_beta_crit}
Here we estimate the maximum thermal relaxation timescale 
$\beta_c$ that allows growth of the VSI. In Appendix \ref{disp_neut_limit}
we derive the following relation between $\beta_c$ and the wave
frequency $\hat{\omega}_c$, \emph{assuming} marginal stability to the
VSI:  
\begin{subequations}\begin{align}
    \left(\hat{\omega}_c\khat\right)^4  =& \left(\hat{\omega}_c\khat\right)^2 
  + M(M+1)\left(1-h^2q^2\khat^2\right) ,\label{relax_cond_simp1}  \\
  \left(\hat{\omega}_c\khat\right)^2 = & \frac{\beta_c}{h q} (\gamma-1)(1+2M)^2
  \left(\hat{\omega}_c\khat\right) \label{relax_cond_simp2}\\
  &- 2M(M+1) . \notag
\end{align}\end{subequations}
These equations consider $\khat^2\gg 1$, $M\lesssim O(1)$; and assume 
$|\hat{\omega}\khat| = O(1)$ and $\beta_c\ll 1$.   Note that
Eq. \ref{relax_cond_simp1} reduces to the
dispersion relation for low-frequency inertial waves in the absence of
vertical shear (see Appendix \ref{stable_novshear} for details).

In Appendix \ref{max_cool}, we find that %if $|hq\khat|^2\leq 1$ then 
\begin{align}
  |hq\khat|^2 \leq 1 \Rightarrow \frac{d\beta_c}{dM} < 0 \quad \forall
  M\geq 0. \label{bcrit_gen}
\end{align}
Eq. \ref{bcrit_gen} indicates that higher $M$ modes have lower $\beta_c$,
i.e.\ require faster cooling for VSI growth. This trend is confirmed
numerically in \S\ref{therm_relax_eff}.

@@

We are most interested in the longest cooling time which allows growth for any $M$.  
This criterion is clearly set by the fundamental mode, $M = 0$. It is straight
forward to solve Eq. \ref{relax_cond_simp1} --- \ref{relax_cond_simp2}
for $\beta_c(M=0)  \equiv \beta_\mathrm{crit}$ in this special case. We thus find the cooling criterion for  
VSI growth is  
 \begin{align}\label{iso_vsi_cond}
   \beta <   \beta_\mathrm{crit}  \equiv
   \frac{h|q|}{\gamma-1} . 
 \end{align}
 The thin disk approximation, $h \ll 1$, indicates that $\beta_\mathrm{crit} \ll
 1$, as assumed to obtain Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2}. 
 We heuristically explain $\beta_\mathrm{crit}$ in \S\ref{vsi_require}, and numerically
 test its validity in \S\ref{bcrit_num_test}.

We comment that the expression for $\beta_\mathrm{crit}$ may in fact 
be obtained without assuming it is much less than unity from the onset or 
restrictions on $| h q \khat|$.  This is clarified in Appendix
\ref{bcrit_alt}.

>>>>

\subsection{An upper limit to the cooling time}\label{iso_vsi_beta_crit}
Here we estimate the maximum thermal relaxation timescale 
$\beta_c$ that allows growth of the VSI. In Appendix \ref{disp_neut_limit}
we derive the following relation between $\beta_c$ and the wave
frequency $\hat{\omega}_c$, \emph{assuming} marginal stability to the
VSI:  
\begin{subequations}\begin{align}
    \left(\hat{\omega}_c\khat\right)^4  =& \left(\hat{\omega}_c\khat\right)^2 
  + M(M+1)\left(1-h^2q^2\khat^2\right) ,\label{relax_cond_simp1}  \\
  \left(\hat{\omega}_c\khat\right)^2 = & \frac{\beta_c}{h q} (\gamma-1)(1+2M)^2
  \left(\hat{\omega}_c\khat\right) \label{relax_cond_simp2}\\
  &- 2M(M+1) . \notag
\end{align}\end{subequations}
These equations consider $\khat^2\gg 1$ and %, $M\lesssim O(1)$; 
assumes $|\hat{\omega}\khat| $ is $O(1)$ and $\beta_c\ll 1$.   Note that 
Eq. \ref{relax_cond_simp1} reduces to the  
dispersion relation for low-frequency inertial waves in the absence of
vertical shear (see Appendix \ref{stable_novshear} for details). 
%marginal stability requires hqk \leq 1

We are most interested in the longest cooling time which allows growth
for any $M$. In Appendix \ref{max_cool}, we find that if
$|hq\khat|\leq 1$, then $\beta_c$ decreases with increasing $M$.   
%\begin{align}
%  |hq\khat|^2 \leq 1 \Rightarrow \frac{d\beta_c}{dM} < 0 \quad \forall
%  M\geq 0. \label{bcrit_gen}
%\end{align}
%Eq. \ref{bcrit_gen} indicates that higher $M$ modes have lower $\beta_c$,
%i.e.\ require faster cooling for VSI growth. This trend is confirmed
%numerically in \S\ref{therm_relax_eff}.  
The VSI criterion is then set by $\beta_c$ for the
fundamental mode ($M = 0$), for which the exact solution to 
Eq. \ref{relax_cond_simp1} --- \ref{relax_cond_simp2} is
$\hat{\omega}_c\khat = \beta_c(\gamma-1)/hq = -1$. We thus find the
cooling criterion for VSI growth is    
 \begin{align}\label{iso_vsi_cond}
   \beta <   \beta_\mathrm{crit}  \equiv
   \frac{h|q|}{\gamma-1} . 
 \end{align}
 The thin disk approximation, $h \ll 1$, indicates that $\beta_\mathrm{crit} \ll
 1$, as assumed to obtain Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2}. 
 We heuristically explain $\beta_\mathrm{crit}$ in \S\ref{vsi_require}, and numerically
 test its validity in \S\ref{bcrit_num_test}.

% This is clarified in Appendix
% \ref{bcrit_alt}.

@@
